### 2015-01-20 src/discussion.Rnw
merging result and discussion

\section{Discussion}
\label{sec:discussion}

We will analyze each of the different types of mutation reduction strategies in
detail, and summarize the broad patterns we see at the end.

@@

For N-selection, which is given in Table~\ref{tbl:nselection}, The best
utility was on removal of \Pitnvmc, \Pitrv, \Pitic, \Pitdc, and \Pitnc which
resulted in a test utility advantage of 2.67\%. It also have the best positive
strategy effectiveness of 0.29\%. However, the difference was not significant
using t-tests in Table~\ref{tbl:ttests} $p-value > 0.01$.~\footnote{The
difference between Table~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
is due to test or mutant number being zero for baseline, and hence remvoed
for computing percentage}.

>>>>

\section{Results}
\label{sec:results}

This section present the result of our experimenting different
mutation selection techniques described in Section \ref{sec:methodology}. 
Each experiment has been done multiple times (at least ten times).
We will analyze each of the different types of mutation reduction 
strategies in detail, and summarize the broad patterns we see at 
the end.

@@

For N-selection, which is given in Table~\ref{tbl:nselection}, 
The best utility was on removal of \Pitnvmc, \Pitrv, \Pitic, 
\Pitdc, and \Pitnc which resulted in a test utility advantage 
of 2.67\%. It also have the best positive
strategy effectiveness of 0.29\%. However, the difference was 
not significant using t-tests in Table~\ref{tbl:ttests} 
$p-value > 0.01$.~\footnote{The difference between Table
~\ref{tbl:nselection} and Table~\ref{tbl:ttests}
is due to test or mutant number being zero for baseline, 
and hence remvoed for computing percentage}.

### 2015-01-20 src/introduction.Rnw
merging result and discussion

\noindent\textbf{Organization.} Section~\ref{sec:related} describes the
research in mutation reduction strategies. Section~\ref{sec:methodology}
 discusses the sampling and operator
selection strategies we study in detail. The analysis is given in
Section~\ref{sec:analysis}, and the results of our experiment are given in
Section~\ref{sec:results}, followed by detailed discussion of what these
results imply in Section ~\ref{sec:discussion}.

>>>>

\noindent\textbf{Organization.} Section~\ref{sec:related} describes the
research in mutation reduction strategies. Section~\ref{sec:methodology}
 discusses the sampling and operator
selection strategies we study in detail. The analysis is given in
Section~\ref{sec:analysis}, and the results of our experiment are detailed in
Section~\ref{sec:results}. Section ~\ref{sec:conclusion} concludes the paper.

### 2015-01-20 src/paper.Rnw
merging result and discussion

<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<threats, child='threats.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
%\FloatBarrier
%\clearpage

>>>>

<<analysis, child='analysis.Rnw'>>=
@
%<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<threats, child='threats.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
%\FloatBarrier
%\clearpage
